Improving the Replicability of Psychological Science Through Pedagogy

### 2017-05-18 paper/paper.Rmd
Put borders around points

p1 <- ggplot(d,aes(x=original_ES_d,y=rep_es)) +
  geom_point(alpha = .8, 
             aes(color=replicated_TA_factor, size = collected_n)) +
  # geom_text_repel(aes(label = first_author_name), size = 2, force = 2) +
  scale_x_continuous(limits = c(0, 1), 
                breaks = c(.1, .3, .5, .7, .9)) +
  scale_y_continuous(limits = c(0, 1), 
                breaks = c(.1, .3, .5, .7, .9)) +
  geom_abline(slope = 1, intercept = 0, linetype = 2) +
  geom_smooth(method = "lm", se=FALSE, colour="#657b83") +
  xlab("Orig. effect size (r)") + 
  ylab("Rep. effect size (r)") + 
  theme_bw(base_size=10) + theme(legend.position="bottom", aspect.ratio = 1) + 
  scale_size(name = "Rep. N") +
  scale_color_manual(values = colorMap, guide = FALSE)  +
  #scale_color_solarized(name = "Subj. rep. rating") +
  guides(size=guide_legend(order = 1, direction = "horizontal", byrow=TRUE))

@@

p2 <- ggplot(tstatDF, aes(x = origBF, y = repBF)) +
  geom_point(alpha = .8, aes(size = df_ratio, 
                             col = replicated_TA_factor)) +
  geom_smooth(method = "lm", se = FALSE, colour="#657b83") +
  geom_abline(slope = 1, intercept = 0, linetype = 2) +
  xlab("Orig. Bayes Factor") + 
  ylab("Rep. Bayes Factor") + 
  scale_x_log10(limits = c(10**-1.75, 10**11), 
                breaks = c(1/10, 1, 10, 100, 1e+3, 1e+6, 1e+9),
                labels = c(".1", "1", "10","100", "1e3", 
                           "1e6","1e9")) +
  scale_y_log10(limits = c(10**-1.75, 10**11),
                breaks = c(1/10, 1, 10, 100, 1e+3, 1e+6, 1e+9),
                labels = c(".1", "1", "10","100", "1e3", 
                           "1e6","1e9")) + 
  theme_bw(base_size=10) + 
  scale_size_continuous(breaks=c(.5, 2, 5),name = "Rep. df/Orig. df") + 
  scale_color_manual(values = colorMap, guide = F) +
  theme(legend.position="bottom", aspect.ratio = 1) + 
  guides(size=guide_legend(direction = 'horizontal'))

plotrow <- plot_grid(p1, p2, labels = c("A", "B"))
legend <- get_legend(
  p2 + 
    theme(legend.position="bottom") + 
    guides(color = guide_legend(title = "Subjective replication rating", 
                                direction = 'horizontal',
                                override.aes = list(size=10)),
           size = FALSE)
)
plot_grid(plotrow, legend, ncol = 1, rel_heights = c(1, .2))
```

>>>>

p1 <- ggplot(d,aes(x=original_ES_d,y=rep_es)) +
  geom_point(alpha = .8, pch=21,
             aes(fill=replicated_TA_factor, size = collected_n)) +
  # geom_text_repel(aes(label = first_author_name), size = 2, force = 2) +
  scale_x_continuous(limits = c(0, 1), 
                breaks = c(.1, .3, .5, .7, .9)) +
  scale_y_continuous(limits = c(0, 1), 
                breaks = c(.1, .3, .5, .7, .9)) +
  geom_abline(slope = 1, intercept = 0, linetype = 2) +
  geom_smooth(method = "lm", se=FALSE, colour="#657b83") +
  xlab("Orig. effect size (r)") + 
  ylab("Rep. effect size (r)") + 
  theme_bw(base_size=10) + theme(legend.position="bottom", aspect.ratio = 1) + 
  scale_size(name = "Rep. N") +
  scale_fill_manual(values = colorMap, guide = FALSE)  +
  #scale_color_solarized(name = "Subj. rep. rating") +
  guides(size=guide_legend(order = 1, direction = "horizontal", byrow=TRUE))

@@

p2 <- ggplot(tstatDF, aes(x = origBF, y = repBF)) +
  geom_point(alpha = .8, pch=21, aes(size = df_ratio, 
                             fill = replicated_TA_factor)) +
  geom_smooth(method = "lm", se = FALSE, colour="#657b83") +
  geom_abline(slope = 1, intercept = 0, linetype = 2) +
  xlab("Orig. Bayes Factor") + 
  ylab("Rep. Bayes Factor") + 
  scale_x_log10(limits = c(10**-1.75, 10**11), 
                breaks = c(1/10, 1, 10, 100, 1e+3, 1e+6, 1e+9),
                labels = c(".1", "1", "10","100", "1e3", 
                           "1e6","1e9")) +
  scale_y_log10(limits = c(10**-1.75, 10**11),
                breaks = c(1/10, 1, 10, 100, 1e+3, 1e+6, 1e+9),
                labels = c(".1", "1", "10","100", "1e3", 
                           "1e6","1e9")) + 
  theme_bw(base_size=10) + 
  scale_size_continuous(breaks=c(.5, 2, 5),name = "Rep. df/Orig. df") + 
  scale_fill_manual(values = colorMap, guide = F) +
  theme(legend.position="bottom", aspect.ratio = 1) + 
  guides(size=guide_legend(direction = 'horizontal'))

plotrow <- plot_grid(p1, p2, labels = c("A", "B"))
legend <- get_legend(
  p2 + 
    theme(legend.position="bottom") + 
    guides(fill = guide_legend(title = "Subjective replication rating", 
                                direction = 'horizontal',
                                override.aes = list(size=8)),
           size = FALSE)
)
plot_grid(plotrow, legend, ncol = 1, rel_heights = c(1, .2))
```
